Reaction-Advection-Diffusion Models of Air Pollution

### 2024-04-28 paper.tex
11.25

An example of the output of the algorithm is shown below:

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{inmap2.png}
    \caption{The result of the model when running with $\text{PM}_{2.5}$ as the specified pollutant.}
    \label{fig:grid2}
 \end{figure}

>>>>

InMAP does this process for calculating the wind velocity in the advection term of equation (13). InMAP splits each variable
into three parts:

\begin{equation}
    v = \overline{x} + \tilde{x} + v', C = \overline{C} + \tilde{C} + C'    
\end{equation}

where $\tilde{x} \text{ and }  \tilde{C}$ are deviations calculated by WRF-Chem, and $v' \text{ and }  C'$ are other deviations.

Substituting this decomposition into equation (13) yields:

$$
    \nabla \cdot (vC_i) = \nabla \cdot ((\overline{x} + \tilde{x} + x')(\overline{C_i} + \tilde{C_i} + C_i'))
$$

$$
    =  \nabla \cdot (\overline{x}\overline{C_i}) +  \nabla \cdot (\overline{x}\tilde{C_i}) + \nabla \cdot (\overline{x}C_i') 
    +  \nabla \cdot (\tilde{x}\overline{C_i}) + \nabla \cdot (\tilde{x}\tilde{C_i}) + \nabla \cdot (\tilde{x}C_i')
    + \nabla \cdot (x'\overline{C_i}) + \nabla \cdot (x'\tilde{C_i}) + \nabla \cdot (x'C_i')
$$

We now apply the Reynolds averaging rules to remove four of the above terms to yield:

\begin{equation}
    =  \nabla \cdot (\overline{x}\overline{C_i}) +  \nabla \cdot (\tilde{x}\tilde{C_i}) + \nabla \cdot (\tilde{x}C_i')  + \nabla \cdot (x'\tilde{C_i}) + \nabla \cdot (x'C_i')
\end{equation}

We now have to discretize the first term of the above equation. InMAP chooses to do that using the following equation:

$$
\frac{\Delta C_i}{\Delta t} = \begin{cases}
    \frac{1}{\Delta x}\sum\limits_{j=1}^{n_y} U_iC_{i,j}n_j, & \text{if }U_i \geq 0 \\
    \frac{1}{\Delta x}\sum\limits_{j=1}^{n_y} U_iC_{i,j}, & \text{if }U_i < 0
    \end{cases} 
$$

We now have most of the required information verified to begin running InMAP. To demonstrate further, an example of the output of the algorithm is shown below:

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{inmap2.png}
    \caption{The result of the model when running with $\text{PM}_{2.5}$ as the specified pollutant.}
    \label{fig:grid2}
 \end{figure}

\subsection{Configuring InMAP}

InMAP allows the user to have lots of flexibility regarding configuring the model. After downloading the executable,
the program prompts the user to provide a configuration file. Within this file, there exists many configuration options,
some of which are shown below:

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{code.png}
    \caption{A few of the configuration options available. The total $\text{PM}_{2.5}$ concentration is composed of multiple
    sources. The total deaths per ethnicity are also shown.}
    \label{fig:grid2}
 \end{figure}

The model can then be executed. The execution time of the model is still quite long, so it is easier to access InMAP via an API.

\section{Results}

To obtain our results, we utilized an API created by the company WattTime. WattTime combines marginal emission rates with InMAP's results
to produce a figure representing the health damage per MWh. To better understand how marginal emissions rates impact damage to human health caused
by emissions, consider the states of California and Mississippi. California has a much cleaner grid with a higher access to renewable energy (see below), 
so if a spike in demand occurs for energy production, it is much easier to compensate that demand with renewable energy. However,
in Mississippi, only 3 percent of the energy produced is renewable. In addition, the state consumes three times more energy than it produces.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{renewables.png}
    \caption{A snapshot of California's grid makeup according to CAISO, California's Independent Service Operator.}
    \label{fig:grid2}
 \end{figure}
